{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-14 paper/paper.tex
added paragraph about histories
added first part of scheduler definition

>>>>

To complete our multithreaded setup we need a scheduler. The scheduler will
operate on histories. A history is a list of pairs $(tid, l$), where $tid \in
Thread$ and $l \in Level$. In this history all threads chosen by the scheduler
are recorded.

At this point no concrete scheduler is defined to make the framework applicable
for a wide class of schedulers. A scheduler is in this class iff it can be
modeled as a function $pickt: ConcState \times History \rightharpoonup Thread$
which satisfies the following constraints:
